Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-04-17 LCAforActiveSonarImaging/lca.tex
More on LCA
Another day, no progres

Most modern active sonar imaging systems are usually far better at resolving details in range than in the angular direction. This is because it is relatively cheap and easy to collect a long and well sampled temporal representation of the incoming wavefield, but hard to do so spatially. It would require a very large array with a lot of sensors, which is costly, complex and impractical. Alternatively, a larger array can be synthesized from several successive pings recorded by a smaller physical array using a technique called synthetic aperture sonar (SAS). Unfortunately, not many of these systems exist due to the difficulty of navigating with sufficiently high precision under water.

It would be more convenient to avoid 
Hence, if the angular resolution can be improved by  the angular resoliutio
Since A solution that is more convenient, cost-effective and simple solution would be to

@@

>>>>

Most modern active sonar imaging systems are usually far better at resolving details in range than in the angular direction. This is because it is relatively cheap and easy to collect a long and well sampled temporal representation of the incoming wavefield, but hard to get the spatial equivalent. It would require a very large array with a lot of sensors, which is costly, complicated and impractical. An alternative is to synthesize a large array from a small array by coherently combining data from successive pings. This technique is called synthetic aperture sonar (SAS). Unfortunately, it is very challenging to navigate with sufficient precision under water this is a very challenging task due to the difficulty of navigating with sufficiently high precision under water.

Due to the challenges of solving this issue with hardware, a lot of research is put into improving the image reconstruction algorithms. At the heart of these is a technique called beamforming, which seeks to estimate scattering strength for each pixel location. It does this by applying a suitable set of the estimate the involves applying a suitable set of delays and weights to the sensors to coherently combine the sensors' data using a seeks to where focus is obtained in  the where delays and weights are used on the array's channels to form a coherent combination ly combine

It would be more convenient 
Hence, if the angular resolution can be improved by  the angular resoliutio
Since A solution that is more convenient, cost-effective and simple solution would be to

Reminder: Always hit you equal in war, +/- 2 ranks. Example: If your position on the war map is #20, then pick a target in the range #18-#22. Only exception is for our top 10-15 players, which may use second attack for cleanup.

@@

% \begin{table}[!b]\centering%\normalsize
% \begin{tabular}[c]{l r r r@{}  l}\hline
% \rowcolor{tabBlue} & \multicolumn{1}{>{\columncolor{tabBlue}}c}{\bf B$_\text{arith}$} & \multicolumn{1}{>{\columncolor{tabBlue}}c}{\bf B$_\text{mem}$} & \multicolumn{2}{>{\columncolor{tabBlue}}c}{\bf B$_\text{mem}$/B$_\text{arith}$} \\\hline
% Arithmetic & 1.03 Tflop/s & & &\\
% Global memory & & 36 Gfloats/s & \hspace{30pt} 1 &:30 \\
% Shared memory & & 257 Gfloats/s & 1 &:4 \\
% Registers & & $>$1.5 Tfloats/s & $>$3 &:2~\cite{Vasilyy}
% \end{tabular}
% \caption{Nvidia Quadro 6000: Memory throughput, $B_{\lowercase{\text{mem}}}$, compared to arithmetic throughput, $B_\text{arith}$.}\label{throughputs}
% \end{table}%

\newcommand\cc[1]{\multicolumn{1}{>{\columncolor{tabBlue}}c}{\bf #1}}
\begin{table}[!b]\centering%\normalsize
\begin{tabular}[c]{l r r r@{}  r r r}\hline
\rowcolor{tabBlue} & \cc{Resolution} & \cc{S} & \cc{$\beta$} & \cc{$\varphi^*$} &  \cc{N$_\beta$} & \cc{N$_\varphi$} \\\hline
& 50\%  & 28 & [0,3] & \hspace{.15cm} 50\% & 2 & 3 \\
& 50\%  & 28 & [0,6] & \hspace{.15cm} 50\% & 2 & 3 \\
& 50\%  & 28 & [0,9] & \hspace{.15cm} 50\% & 2 & 3 \\
& 100\% & 32 &  &:30 \\
& 150\% & 32 & 1 &:4\\
\end{tabular}\\
* Steering is relative to the -3dB width of the window being applied.
\caption{Qualitative study}\label{parameter_study}
\end{table}%
